Meeting the Challenges of Modeling Astrophysical Thermonuclear Explosions: \castro, \maestro, and the \amrex\ Astrophysics Suite

### 2017-10-09 astronum_2017/astronum-amrex.tex
add plot
updated scaling
more progress

\begin{figure}[t]
\centering
\includegraphics[width=0.48\linewidth]{titan_edison_maestro_scaling}
\includegraphics[width=0.48\linewidth]{summitdev_scaling} \\
\includegraphics[width=0.48\linewidth]{castro_scaling}
\caption{\label{fig:scaling} (left) \maestro\ strong scaling on NERSC edison
and OCLF titan for a 3-d XRB problem.  Two different problem sizes are show.
(right) \starlord\ scaling across nodes on the OLCF summitdev platform, using
up to 4 GPUs per node.}
\end{figure}

@@

Castro scaling is a placeholder...

@@

Figure~\ref{fig:scaling} shows the performance of \starlord\ on the
summitdev platform at OLCF\footnote{summitdev consists of 2 IBM Power8
  processors and 4 Nvidia Pascal GPUs per node.}.  The highest GPU
count (128) corresponds to 32 nodes on summitdev.  We see a nearly
linear speedup with the number of GPUs, indicating good weak scaling
on this machine.  Efforts are underway to complete the port of the GPU
developments into \castro.

>>>>

\begin{figure}[t]
\centering
\includegraphics[width=0.48\linewidth]{titan_edison_maestro_scaling}
\begin{minipage}[b]{0.48\linewidth}
\caption{\label{fig:maestro_scaling} \maestro\ strong scaling on NERSC
  edison and OLCF titan for a 3-d XRB problem.  Two different problem
  sizes are shown.\vspace{2em}}
\end{minipage}
\end{figure}

\begin{figure}[t]
\centering
\includegraphics[width=0.48\linewidth]{sedov_scaling}
\includegraphics[width=0.48\linewidth]{wdmerger_scaling}
\caption{\label{fig:castro-scaling} (left) \castro\ strong scaling on OLCF titan
for a pure hydro (Sedov) problem; (right) \castro\ strong scaling
on OLCF titan for a hydro + Poisson gravity (wdmerger) problem.}
\end{figure}

\begin{figure}[t]
\centering
\includegraphics[width=0.48\linewidth]{summitdev_scaling}
\includegraphics[width=0.48\linewidth]{cori_scaling}
\caption{\label{fig:knl-gpu-scaling} \castro\ scaling on new architectures.}
\end{figure}

@@

Figure~\ref{fig:castro-scaling}

@@

Figure~\ref{fig:knl-gpu-scaling} shows the performance of \starlord\ on the
summitdev platform at OLCF\footnote{summitdev consists of 2 IBM Power8
  processors and 4 Nvidia Pascal GPUs per node.}.  The highest GPU
count (128) corresponds to 32 nodes on summitdev.  We see a nearly
linear speedup with the number of GPUs, indicating good weak scaling
on this machine.  Efforts are underway to complete the port of the GPU
developments into \castro.
